Detection of defects in additive manufacturing from a single x-ray projection using the empirical null filter

### 2019-08-27 reports/paper1/paper.tex
Use 1 sigma confidence interval
Comment on time change in paper

The running times for the empirical null filter with radius \SI{50}{\pixel} were measured to be \SI[separate-uncertainty = true]{26.72(35)}{\second}. This was compared to simpler filters such as the mean-variance filter which normalises the statistics using the sample mean and sample standard deviation. Running times of \SI[separate-uncertainty = true]{0.0100(12)}{\second} were achieved using the mean-variance filter. With both of these filters, running time increased with kernel radius.

@@

\begin{figure}
  \centering
  \includegraphics[width=0.49\textwidth]{../figures/inference/defectSquare2Example_imageContaminated.eps}
  \caption{A $\SI{256}{\pixel}\times \SI{256}{\pixel}$ contaminated Gaussian image with a $\SI{30}{\pixel} \times \SI{30}{\pixel}$ square defect. The null and alternative distributions are $Z_{x,y}|H_{0,x,y}\sim\normal(\mu_{0,x,y},2^2)$ and $Z_{x,y}|H_{1,x,y}\sim\normal(\mu_{0,x,y}+6,2^2)$ respectively where $\mu_{0,x,y}=0.01(x-x_0)+0.01(y-y_0)$ and $(x_0,y_0)$ is the centre of the image.}
  \label{fig:inference_defectSquare2Example}
\end{figure}

>>>>

The running times for the empirical null filter increased with kernel radius. Compared to typical filters, say the mean and variance filter, the empirical null filter is a number of magnitudes slower. The main bottleneck is the evaluation of the density estimate, each step in the Newton-Raphson required the evaluation of $\pi r^2$ data points.

@@

\begin{figure}
  \centering
  \includegraphics[width=0.49\textwidth]{../figures/inference/DefectExampleSquare40_imageContaminated.eps}
  \caption{A $\SI{256}{\pixel}\times \SI{256}{\pixel}$ contaminated Gaussian image with a $\SI{30}{\pixel} \times \SI{30}{\pixel}$ square defect. The null and alternative distributions are $Z_{x,y}|H_{0,x,y}\sim\normal(\mu_{0,x,y},2^2)$ and $Z_{x,y}|H_{1,x,y}\sim\normal(\mu_{0,x,y}+6,2^2)$ respectively where $\mu_{0,x,y}=0.01(x-x_0)+0.01(y-y_0)$ and $(x_0,y_0)$ is the centre of the image.}
  \label{fig:inference_defectSquare2Example}
\end{figure}
